Titeln på avhandlingens språk

### 2023-04-23 glossary.tex
scope draft
relwork
scope
working on intro

%! suppress = MissingImport
\newacronym[longplural={Wearable Cognitive Assistants}]{WCA}{WCA}{Wearable Cognitive Assistance}
\newacronym[longplural={Augmented Realities}]{AR}{AR}{Augmented Reality}
\newacronym[longplural={Virtual Realities}]{VR}{VR}{Virtual Reality}
\newacronym[longplural={eXtended Realities}]{XR}{XR}{eXtended Reality}
\newacronym[longplural={Mixed Realities}]{MR}{MR}{Mixed Reality}
\newacronym{GPU}{GPU}{Graphical Processing Unit}
\newacronym{FPS}{FPS}{Frames Per Second}
\newacronym{DNN}{DNN}{Deep Neural Network}
\newacronym{CPS}{CPS}{Cyber-Physical System}
\newacronym[prefixfirst={a\ }, prefix={an\ }]{NCS}{NCS}{Networked Control System}
%\acroindefinite{NCS}{an}{a}

@@

\newacronym{CSMA/CD}{CSMA/CD}{Carrier-Sense Multiple Access with Collision Detection}

@@

@@

\newacronym{VLAN}{VLAN}{Virtual Local-Area Network}

@@

\newacronym{O-RAN}{O-RAN}{Open Radio Access Network}

@@

\newacronym{OEDL}{OEDL}{\acs{OMF} Experiment Description Language}

@@

\newacronym{MAR}{MAR}{Mobile \acs{AR}}

@@

\newacronym{CCDF}{CCDF}{Complementary \acs{CDF}}

@@

\newacronym{ECDF}{ECDF}{Empirical \acs{CDF}}

@@

>>>>

%! suppress = MissingImport
\newacronym[longplural={Wearable Cognitive Assistants}]{WCA}{WCA}{Wearable Cognitive Assistance}
\newacronym[longplural={Augmented Realities}]{AR}{AR}{Augmented Reality}
\newacronym[longplural={Virtual Realities}]{VR}{VR}{Virtual Reality}
\newacronym[longplural={eXtended Realities}]{XR}{XR}{eXtended Reality}
\newacronym[longplural={Mixed Realities}]{MR}{MR}{Mixed Reality}
\newacronym{MAR}{MAR}{Mobile \nestedgls{AR}}
\newacronym{GPU}{GPU}{Graphical Processing Unit}
\newacronym{FPS}{FPS}{Frames Per Second}
\newacronym{DNN}{DNN}{Deep Neural Network}
\newacronym{CPS}{CPS}{Cyber-Physical System}
\newacronym[prefixfirst={a\ }, prefix={an\ }]{NCS}{NCS}{Networked Control System}

@@

\newacronym{CSMA}{CSMA}{Carrier-Sense Multiple Access}
\newacronym{CSMA/CD}{CSMA/CD}{\nestedgls{CSMA} with Collision Detection}

@@

\newacronym{GCP}{GCP}{Google Cloud Platform}

@@

% \newacronym{LAN}{LAN}{Local Area Network}
\newacronym{VLAN}{VLAN}{Virtual \nestedgls{LAN}}

@@

\newacronym{RAN}{RAN}{Radio Access Network}
\newacronym{O-RAN}{O-RAN}{Open \nestedgls{RAN}}

@@

\newacronym{OEDL}{OEDL}{\nestedgls{OMF} Experiment Description Language}

@@

@@

\newacronym{CCDF}{CCDF}{Complementary \nestedgls{CDF}}

@@

\newacronym{ECDF}{ECDF}{Empirical \nestedgls{CDF}}

@@

\newacronym{PD}{PD}{Proportional-Differential}
\newacronym{PID}{PID}{Proportional-Integral-Differential}
\newacronym{SDK}{SDK}{Software Development Kit}
\newacronym{YCSB}{YCSB}{Yahoo! Cloud Serving Benchmark}
\newacronym{ITS}{ITS}{Intelligent Transportation System}
\newacronym{OOS}{OoS}{Out-of-Scope}
\newacronym{OMNET}{OMNeT++}{Objective Modular Network Testbed in C++}
\newacronym{ns2}{ns-2}{network simulator 2}
\newacronym{ns3}{ns-3}{network simulator 3}
\newacronym{IRB}{IRB}{Institutional Review Board}
\newacronym{IaaS}{IaaS}{Infrastructure-as-a-Service}
